Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-24 analysis/paper/paper.Rmd
Bug fix for NA in Biplot legend

# this block of code below shows one way to discretize cortex percentage
# into three groups. We need to explore other cutoffs, and other grouping
# variables besides dorsal cortex. This code below is a good template for
# starting these explorations
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 11, 60) ~ "Secondary",
             between(dorsal_cortex_perc, 61, 100) ~ "Primary"
           ))

>>>>

# this block of code below shows one way to discretize cortex percentage
# into three groups. We need to explore other cutoffs, and other grouping
# variables besides dorsal cortex. This code below is a good template for
# starting these explorations
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 60) ~ "Secondary",
             between(dorsal_cortex_perc, 61, 100) ~ "Primary"
           ))
